---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Travis build status](https://travis-ci.org/kvantas/missTune.svg?branch=master)](https://travis-ci.org/kvantas/missTune)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/kvantas/missTune?branch=master&svg=true)](https://ci.appveyor.com/project/kvantas/missTune)
[![Coverage status](https://codecov.io/gh/kvantas/missTune/branch/master/graph/badge.svg)](https://codecov.io/github/kvantas/missTune?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/missTune)](https://cran.r-project.org/package=missTune)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

# missTune

This package is an alternative implementation of the `missForest` and `missRanger` packages using tuned Random Forests. The `tuneRF` function from the `randomForest` is used internally to find the optimal `mtry` parameter.

## Installation

You can install the development version from Github with:

``` r
# install.packages("devtools")
devtools::install_github("kvantas/missTune")

```

## Example

This is a basic example about infilling a dataset.

```{r "infill_iris"}
library(missTune)
# create random na values
iris_na <- generate_na(iris, p = 0.1, seed = 123)

# infill values
res_imp <- miss_tune(x_miss = iris_na, num_trees = 100, verbose = TRUE)


```

Let's view the original data-set with the missing values and the infilled one.

```{r "view data"}
head(iris_na)
head(res_imp$x_imp)
```

And finally let's create a plot with the mean out of bag error during the iterations of the algorithm.

```{r "plot_oob_error"}
library(ggplot2)
mean_errors <- unlist(lapply(res_imp$oob_list, mean))
ggplot()+
  geom_line(aes(x = 1: length(mean_errors), mean_errors)) +
  scale_x_continuous(breaks = 1: length(mean_errors)) + 
  xlab("Iteration") + ylab("Error")+
  theme_bw()
```

## Meta

  Please note that the `missTune` project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
